\documentclass[11pt,a4paper]{article}

% ---------- PAGE ----------
\usepackage[a4paper,margin=0.7in]{geometry}
\usepackage{parskip}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{tikz}
\usepackage{fontawesome5}
\usepackage{hyperref}

% ---------- FONT ----------
\setmainfont{Montserrat}

% ---------- COLORS ----------
\definecolor{accent}{HTML}{4B0082}
\definecolor{darktext}{HTML}{2E2E2E}
\definecolor{lightgray}{HTML}{777777}

% ---------- HYPERLINK SETTINGS ----------
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent,
    filecolor=accent
}

% ---------- DOCUMENT ----------
\begin{document}
\color{darktext}
\setstretch{1.15}

% ---------- HEADER ----------
\begin{tikzpicture}
\node[
    fill=accent,
    rounded corners=6pt,
    inner sep=10pt,
    text width=\linewidth
] {
    \color{white}
    {\Huge \textbf{ANTHONY\hspace{0.3cm}BYAMUGISHA}}\\
    \vspace{2pt}
    {\Large Data and BI Analyst}
};
\end{tikzpicture}

\vspace{4pt} % Reduced from 8pt to 4pt to fix space above email

% ---------- CONTACT (LEFT ALIGNED) ----------
\begin{flushleft}
\faEnvelope\ \href{mailto:byamugishanthony@gmail.com}{byamugishanthony@gmail.com}\\
\faPhone\ +256 748 161 708\\
\faMapMarker*\ Makerere, Kampala, Uganda\\
\faLinkedin\ \href{https://linkedin.com/in/byamugisha-anthony}{linkedin.com/in/byamugisha-anthony}\\
\faGlobe\ \href{https://anthonybyamugishadata-analyst.vercel.app}{anthonybyamugishadata-analyst.vercel.app}\\
\faGithub\ \href{https://github.com/anthonybyamugisha}{github.com/anthonybyamugisha}
\end{flushleft}

\vspace{6pt}
{\color{accent}\hrule}
\vspace{12pt}

% ---------- RECIPIENT ----------
To:\\
Hiring Manager\\
Bank of Uganda\\
P.O. Box 7120,\\
Kampala, Uganda

\vspace{6pt}

\textbf{Dear Hiring Manager,}

\vspace{4pt}

I am writing to express my interest in the Data Analyst Internship at the Bank of Uganda. I am eager to contribute my analytical skills while gaining hands-on experience in a professional, data-driven environment.

\vspace{6pt}

I am currently pursuing a Bachelor of Science in Computer Science at Makerere University, where I am in my second year of study. In addition, I am advancing my practical analytics skills through the Data Science Lab at WorldQuant University, where I work with real-world datasets involving data cleaning, exploratory data analysis, and statistical problem-solving. These experiences have provided me with a strong foundation in data analysis, business intelligence, and data visualization.

\vspace{6pt}

I am actively developing proficiency in Power BI, where I design interactive dashboards and reports to track KPIs, analyze performance, and support informed decision-making. I also have working knowledge of Python (Pandas, NumPy, Matplotlib), SQL, and Microsoft Excel, which I use to extract meaningful insights from structured datasets.

\vspace{6pt}

I am highly motivated, detail-oriented, and a fast learner with a strong desire to continuously improve my skills. I believe this internship at the Bank of Uganda would be an excellent opportunity to further develop my analytical capabilities while contributing value to your data and reporting initiatives.

\vspace{8pt}

Thank you for your time and consideration.

\vspace{10pt}

Yours sincerely,\\
\vspace{2pt}
Anthony Byamugisha

\end{document}